---
title: "Loxahatchee 39 Box Stage Model"
output: html_notebook
---
This markdown file runs a user defined model scenario for the 39 Box Stage Model.
  If you modify this markdown file, save the modified file with a new filename 
  (i.e. not as runStage.Rmd).

Set the run output file name and run title in the following code chunk:
```{r echo=FALSE}
  if (exists('filename')) { rm(filename) } # remove old filename if it exists
  # if you don't set filename on the next line it will be given 
  #   the default value '39BoxBase'
  # filename <- 'deleteme' # for example
```

Run the initial scripts to set up the model run:
```{r echo=FALSE, results = 'markup'}
# remove all variables from the environment except "filename"
rm(list = ls()[! ls() %in% "filename"])

# (NOTE: Use command dev.off() in the console to reset the plot window to 
# default settings and clear all plots)

# Load the base model datasets, recreate it if it does not already exist
  # Load required dataframes created by script make_datasets.R
  if (file.exists(file="../Datasets/39-Box-Datasets.Rdata")) {
    load(file="../Datasets/39-Box-Datasets.Rdata")
  } else {
    print('Running make_datasets.R to rebuild file 39-Box-Datasets.Rdata.')
    source('make_datasets.R')
  }

  # load the model functions 
  source("39BoxFunctions.R") 
  
  # load the general model constants 
  source("39BoxBase.R")

# set the name of the output file
  # if the name was not set then use '39BoxBase'
  if (! exists("filename")) { # if the variable "filename" exists
    filename <- '39BoxBase' # file name for the base model run
  } # end if

  # set title of this scenario run
  run.title <- filename
  
```

Make any user defined changes to the model parameters in the following code chunk.
This may alter constants, loaded dataframes, or redefine functions.

Example: Model the impact of increasing water supply flow through the S39 by 20%

      NonReg$S39 <- 1.2*NonReg$S39

Example: Set new model run start and stop dates

      Start.Date <- as.Date('2025-01-01')
      
      Stop.Date  <- as.Date('1995-04-30')

```{r}

  # Start.Date <- as.Date('2025-01-01')  # set an alternative start or stop date
  # Stop.Date  <- as.Date('1995-04-30')
  # nX <- 1 # run with output only at the end of the day

```


The following code chunk runs the model.
  Note: This may take a long time. The model is running if a red button is 
        visible at the top right of the chunk.
```{r}
  model.script <- "39BoxStage.R"
  source(model.script)
  print('model run finished')
```


```{r}
# run a standard set of graphics 
  source('39BoxStageStdGraphs.R')

# __________________________________________________________  
# On the following lines add any user defined final statistical calculations, or graphics
  
 
```
